Supporting Information

### 2016-08-23 portfolio/text/ms.Rmd
Edit text
Edit text and abstract

Individuals relying on natural resources as their primary source of income
often experience high levels of income-variability 
due to the combined effects of environmental and price variation. 
Commercial fishermen are a prime example and
recent work has sought to identify regulations and fishing behaviours 
that can reduce this variability. 
A top candidate has been that fishing higher levels of species diversity
decreases income variability, which is concerning 
given that some fishing regulations and market forces
may be increasingly promoting specialization. 
However, it is unknown if this species-diversity effect 
on income variability holds 
across multiple approaches to diversifying catch,
at the level of individual permit holders,
and across different fishing strategies. 
Here, we simultaneously estimate the effects of three 
methods of diversification for Alaskan fishery permit holders
on revenue and revenue variability:
(1) owning multiple permits, 
(2) owning permits that inherently fish higher species diversity, 
and (3) adjusting species diversity within the constraints of a permit.
We control for changes in effort and other 
residual effects through time.
We find that 
fishing an additional permit is associated with 
lower variability (~XX--XX%) and higher revenue,
fishing permits with higher species diversity reduces risk 
(XX--XX% per unit increase in Simpson's diversity index),
but that changing species diversity within a
permit's constraints has a fishery-dependent effect on revenue and 
is usually (XX%) associated with increased revenue variability.
Our results suggest that the benefit of species diversity
on reducing revenue variability 
is mostly an across-permit effect, not
a benefit that can be easily harnessed by an individual permit holder.
Effective methods of diversification --- 
purchasing additional permits or switching permits ---
are costly and often limited by regulations such as limited entry
programs and individual transferable quotas (ITQs).
Our results suggest ...

@@

<!-- Main message in 25 words or less: -->

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.1\textwidth]{../figs/stan-offset-break-anti-spaghetti.pdf}
\caption{Effects of (A) generalizing and (B) specializing from year to year for
individual permit holders across the `r nstr` most common strategies.
Changing species diversity from year to year 
is associated with higher variability
for individuals within the strategies above the zero line.
Generalizing (A) or specializing (B) is associated with
greater expected revenue to the right of the zero line
and lower expected revenue to the left of the zero line.
These effects are estimated holding
fishing season length constant from year to year.
}
\label{fig:within}
\end{center}
\end{figure}

>>>>

Individuals relying on natural resources as their primary source of income
often experience highly variable income levels 
due to the combined effects of environmental and price variation. 
Commercial fishers are a prime example and
recent work has sought to identify regulations and fishing behaviours 
that can reduce this variability. 
A top candidate has been that fishing higher levels of species diversity
decreases income variability.
However, it is unknown if this species-diversity effect 
on income variability holds 
across multiple approaches to diversifying catch,
at the level of individual permit holders,
and across different fishing strategies. 
Here, we simultaneously estimate the effects of three 
methods of diversification for Alaskan fishery permit holders
on revenue and revenue variability:
(1) owning multiple permits, 
(2) owning permits that inherently fish higher species diversity, 
and (3) adjusting species diversity within the constraints of a permit.
We control for changes in effort and other 
residual effects through time.
We find that 
fishing an additional permit is associated with 
lower variability (~XX--XX%) and higher revenue,
fishing permits with higher species diversity reduces risk 
(XX--XX% per unit increase in Simpson's diversity index),
but that changing species diversity within a
permit's constraints has a fishery-dependent effect on revenue and 
is usually (XX%) associated with increased revenue variability.
At the same time, Alaskan commercial fisheries
have increasingly focussed on 
single-permit (often salmon) fishing strategies
with single-permit fishers earning 
more than multiple-permit fishers
for the first time in 2014.
Our results suggest that the benefit of species diversity
on reducing revenue variability 
is mostly an across-permit effect, not
a benefit that can be easily harnessed by an individual permit holder.
Effective methods of diversification --- 
purchasing additional permits or switching permits ---
are costly and often limited by regulations such as limited entry
programs and individual transferable quotas (ITQs).
Take home ...

@@

<!-- , which is concerning  -->
<!-- given that some fishing regulations and market forces -->
<!-- may be increasingly promoting specialization. -->
<!-- Main message in 25 words or less: -->

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.1\textwidth]{../figs/stan-offset-break-anti-spaghetti.pdf}
\caption{Effects of (A) generalizing and (B) specializing from year to year for
individual permit holders across the `r nstr` most common strategies.
Changing species diversity from year to year 
is associated with higher variability
for individuals within the strategies above the zero line.
Generalizing (A) or specializing (B) is associated with
greater expected revenue to the right of the zero line
and lower expected revenue to the left of the zero line.
These effects are estimated holding
fishing season length constant from year to year.
Dots and line segments represent medians and 
50\% credible intervals of posteriors.
}
\label{fig:within}
\end{center}
\end{figure}

### 2016-08-23 portfolio/text/supp.Rnw
Edit text and abstract

We checked our models with a two-part modelling approach
using the R package lme4.
To do this, we fit the initial model of the mean component $\log(R_{i,t})$
and then fit the second model to the log absolute value of the
residuals, $\log | \widehat{\log(R_{i,t})} - \log(R_{i,t}) |$.
Most importantly, (1) this model does not carry uncertainty
from the first mean-component model to the variance-component model, but
(2) it also leaves the residuals in the mean-component model strongly
heteroskedastic and therefore improperly weights individual data points, and
(3) does not allow for proper modelling of the strategy-level predictor,
$\eta_1$. Nonetheless, it provides a check that our results
from the Stan model are approximately correct and allowed us
to quickly iterate and build intuition about the models.

>>>>

We checked our models with a two-part modelling approach
using the R package lme4.
To do this, we fit the initial model of the mean component $\log(R_{i,t})$
and then fit the second model to the log absolute value of the
residuals, $\log | \widehat{\log(R_{i,t})} - \log(R_{i,t}) |$.
Most importantly, (1) this model does not carry uncertainty
from the first mean-component model to the variance-component model, but
(2) it also leaves the residuals in the mean-component model strongly
heteroskedastic and therefore improperly weights individual data points, and
(3) does not allow for proper modelling of the strategy-level predictors,
$\eta_1$ and $\eta_2$. Nonetheless, it provides a check that our results
from the Stan model are approximately correct and allowed us
to quickly iterate and build intuition about the models.
A version of the Stan model without the variance-component
matched the estimates of the same model in lme4 almost exactly.
